% use the custom resume.cls style
\documentclass{resume}

% document margins
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx} % Include this package in your preamble

\setlength\columnsep{15pt}


% commands
\newcommand{\tab}[1]{\hspace{.1667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Marvin Martin}
\address{\textbf{3+ years of Machine Learning Experience}}
\address{
	Brooklyn, NY 11249 \\
	\href{mailto:mmartin.mmarvin@gmail.com}{mmartin.mmarvin@gmail.com} \\
	+1 (917) 815-9864
}


\begin{document}

	\begin{multicols}{2}

	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{\Large Education}
		\begin{school}{Boston University}{Boston, MA}{M.Sc. in Computer Information Systems}{01/2021}{09/2021}{
			\begin{description}
				\item[$\bullet$]Major:  Data Analytics, GPA 4.0
				\item[$\bullet$]{Relevant Coursework: \\
				Analysis of Algorithms, Big Data Analytics, \\
				Advanced Programming Techniques,  \\
				Machine Learning, and Deep Learning.}
			\end{description}
		}
		\end{school}
		
		\begin{school}{Ecole Centrale d'Electronique}{Paris, FR}{M.Sc. in Computer Information Systems}{09/2018}{12/2020}{
			\begin{description}
				\item[$\bullet$]Major: Data Science, Grade A  (Top 5\%, 16.8/20)
				\item[$\bullet$]{Relevant Coursework: \\
				C Language, Advanced Database, DevOps, Web Dev,\\
				Cloud computing, Mathematics for Data Science,\\
				Calculus, Algebra, Physics, and Signal Processing.}
			\end{description}
		}
		\end{school}
		\begin{school}{INSEEC London}{London, UK}{B.Sc. in Computer Science}{01/2019}{05/2019}{
		}
		\end{school}
		\begin{school}{Heriot-Watt University}{Edinburgh, UK}{B.Sc. in Computer Science}{01/2018}{06/2018}{
		}
		\end{school}
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	WORK EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{\Large Experience}
	
		%----------------------------------------------------
		%	Vic.ai
		%----------------------------------------------------
		\begin{job}{Vic.ai (Startup - Series C)}{New-York, NY, USA}{Machine Learning Engineer}{11/2021}{Present}{
			\link{https://www.vic.ai/}{Vic.ai}builds AI-based autonomous accounting systems.
			\begin{description}
				\item[$\bullet$] Leveraging Large Language Models (LLM) for accounting.
				\item[$\bullet$] Natural Language Processing (NLP) tasks.
				\item[$\bullet$] Build Projects like PO Matching, Invoice Coding, OCR.
				\item[$\bullet$] ML Infrastructure (Lambda, SageMarker, Kubernetes).
				\item[$\bullet$] Data Engineering, Feature Engineering at scale (Ray).
				\item[$\bullet$] Support +20,000 models training bi-weekly (+800\%).
			\end{description}
		}
		\end{job}

		%----------------------------------------------------
		%	Centre Securite Requin
		%----------------------------------------------------
		\begin{job}{Centre Securite Requin}{New-York, NY, USA}{Machine Learning Engineer Consultant}{11/2020}{Present}{
			\link{http://www.info-requin.re/le-centre-securite-requin-r70.html}{CSR}is a public research center that studies shark attacks.
			\begin{description}
				\item[$\bullet$] Computer Vision (CV) for shark classification task.
				\item[$\bullet$] Build Deep Neural Network for underwater (CNN/ViT).
				\item[$\bullet$] Research related to Adversarial Domain Adaptation.
				\item[$\bullet$] Create pipelines using Nifi to classify videos in real time.
				\item[$\bullet$] Investigate model reliability based on weather conditions.
			\end{description}
		}
		\end{job}

		%----------------------------------------------------
		%	HEURITECH
		%----------------------------------------------------
		\begin{job}{Heuritech}{Paris, FR}{Training Data Operator Intern}{04/2020}{08/2020}{
			\link{https://www.heuritech.com/}{Heuritech}builds visual recognition and trend forecasting \\ technologies for fashion industry.
			\begin{description}
				\item[$\bullet$] Ran data engineering tasks to improve datasets. 
				\item[$\bullet$] Trained Deep ConvNets.
				\item[$\bullet$] Active Learning research on acquisition functions.
				\item[$\bullet$] Training metrics investigation.
			\end{description}
		}
		\end{job}
		%----------------------------------------------------
		%	LECTRA
		%----------------------------------------------------
		\begin{job}{Lectra, Innovation Lab}{Bordeaux , FR}{Lab Intern}{05/2019}{06/2019}{
			\link{https://www.lectra.com/fr}{Lectra}develops systems for the textile industry.
			\begin{description}
				\item[$\bullet$] Explored Generative Adversarial Network for fashion.
			\end{description}
		}
		\end{job}
	\end{rSection}
	
	\columnbreak
	
	%----------------------------------------------------------------------------------------
	%	Links
	%----------------------------------------------------------------------------------------
	\begin{rSection}{\Large Links}
			\link{https://www.linkedin.com/in/marvin-martin-00b937120/}{LinkedIn}
			\link{https://github.com/MarvinMartin24}{Github}
			\link{https://medium.com/@martin.marvin}{Medium}
			\link{https://marvinmartin24.github.io/}{Website}
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%	Publications
	%----------------------------------------------------------------------------------------
	\begin{rSection}{\Large Publications}
		\textbf{In progress}: ADA-Shark: A framework for shark detection employing underwater cameras and domain adversarial neural network (Boston University \& CSR). 
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	Projects
	%----------------------------------------------------------------------------------------
	\begin{rSection}{\Large Projects}
	
		%----------------------------------------------------------------------------------------
		%	Projects #1
		%----------------------------------------------------------------------------------------
		\begin{project}{Domain adversarial neural network}{\link{https://github.com/MarvinMartin24/MADA-PL/blob/main/Report/Domain-Adversarial-Training-Report.pdf}{[Report]}}{\link{https://github.com/MarvinMartin24/MADA-PL}{[Code]}}{
			Reproducibility study of the \link{https://jmlr.org/papers/volume17/15-239/15-239.pdf}{DANN} and \link{https://arxiv.org/pdf/1809.02176.pdf}{MADA} papers \\using PyTorch-Lightning.
		}
		\end{project}
		%----------------------------------------------------------------------------------------
		%	Projects #2
		%----------------------------------------------------------------------------------------
		\begin{project}{PySpark neural network from scratch}{\link{https://towardsdatascience.com/pyspark-neural-network-from-scratch-8a19ebad3904}{[Article]}}{\link{https://github.com/MarvinMartin24/PySpark-Neural-Network}{[Code]}}{
		 	Spark implementation of a shallow neural network to classify \\handwritten digits. Gradients are computed via MapReduce.
		}
		\end{project}
		
		%----------------------------------------------------------------------------------------
		%	Projects #3
		%----------------------------------------------------------------------------------------
		\begin{project}{Emotion based Art Generator}{\link{https://medium.com/@martin.marvin/emotion-based-art-generation-using-c-gan-de9abed6fa2f}{[Article]}}{\link{https://github.com/MarvinMartin24/CGAN-Emotion-Art}{[Code]}}{
			Conditional generative adversarial neural network (CGAN) \\trained to generate 64 $\times$ 64 painting images for a selected \\style and emotion.
		}
		\end{project}	
		%----------------------------------------------------------------------------------------
		%	Projects #3
		%----------------------------------------------------------------------------------------

		\begin{project}{Neural Network from Scratch}{\link{https://medium.com/@martin.marvin/emotion-based-art-generation-using-c-gan-de9abed6fa2f}{[Article]}}{\link{https://github.com/MarvinMartin24/CGAN-Emotion-Art}{[Code]}}{
		Mathematics and Numpy code behind 3 Layers Neural \\Network.
		}
		\end{project}	
	\end{rSection}
	
	
	%----------------------------------------------------------------------------------------
	%	Certificate
	%----------------------------------------------------------------------------------------
	\begin{rSection}{\Large Certifications}
		\begin{description}
			\setlength\itemsep{-0.5em}
			\item[$\bullet$] \link{https://www.coursera.org/account/accomplishments/certificate/AD5Z7KGC3QJY}{Generative AI with Large Language Models}
			\item[$\bullet$] \link{https://www.cloudskillsboost.google/public_profiles/01a17435-5a17-40f0-88e0-972d77b2fda5/badges/3950403}{Generative AI Fundamentals}
			\item[$\bullet$] \link{https://app.workera.ai/public/candidate/certificate?code=AUNDCFBV}{Workera Software Engineer Deep Learning Assessment}
			\item[$\bullet$] \link{https://www.coursera.org/account/accomplishments/specialization/certificate/925K8YUCXEW2}{Deep Learning Specialization} 
			\item[$\bullet$] \link{https://www.coursera.org/account/accomplishments/specialization/certificate/MRPQR8RYY89R}{GANs Specialization}	
		\end{description}
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	SKILLS
	%----------------------------------------------------------------------------------------
	\begin{rSection}{\Large Skills}
		\noindent
		 \setlength{\tabcolsep}{2pt}
    \begin{tabularx}{0.50\textwidth}{@{\textbullet\hspace{\labelsep}}lX}
        \textbf{Languages} & Python, Java, Bash, R, C, JavaScript. \\
        \textbf{ML Libraries} & PyTorch, Keras, HuggingFace, Transformers, PEFT, LangChain, OpenAI, LLama-Index, Skit-Learn, Wandb, DVC, OpenCV, CatBoost, PySpark. \\
        \textbf{Monitoring} & Sentry, Datadog, Grafana, Zabbix. \\
        \textbf{Deployment} & Docker, Terraform, Kubernetes, AWS, Git-flow, Circle-ci. \\
        \textbf{Cloud} & AWS (SageMaker, S3, Lambda, Batch, ECS, EFS, SAM), GCP, Azure, Ray. \\
        \textbf{Databases} & PostgreSQL, Redis, MongoDB, Firebase, Chroma, Pinecone. \\
        \textbf{Communication} & Leadership, Public-Speaking, Scrum, Jira, Cross-Team communication. \\
    \end{tabularx}
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	LANGUAGES
	%----------------------------------------------------------------------------------------
	\begin{rSection}{\Large Languages}
		\textbf{English}:  Fluent \hspace{1ex} \textbf{French}: Native \hspace{1ex} \textbf{Spanish}:  Novice
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	EXTRA
	%----------------------------------------------------------------------------------------
	\begin{rSection}{\Large ACTIVITIES \& LEADERSHIP}
		\textbf{Comedian, Stuntman}: Performed in \link{https://www.youtube.com/channel/UCorBR38MbWKo92Go3dBpv2Q}{Timeo} in front of 1000 people, 3 times a week as a skateboarder (2016).\\
		\textbf{Sports}: Skateboard (Instructor), Surf, and Slackline.\\
		\textbf{Achievements}: 300km in 3 days on a longboard.
	\end{rSection}
	
	\end{multicols}
\end{document}
