% use the custom resume.cls style
\documentclass{resume}

% document margins
\usepackage[left=0.3in,top=0.4in,right=0.3in,bottom=0.4in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

% commands
\newcommand{\tab}[1]{\hspace{.1667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Marvin Martin}
\address{Paris, France}
\address{(+33) 6 85 47 46 44 \\ \href{mailto:mmartin.mmarvin@gmail.com}{mmartin.mmarvin@gmail.com}}
\address{\link{https://marvinmartin24.github.io/}{Website} \\ \link{https://www.linkedin.com/in/marvin-martin-00b937120/}{LinkedIn} \\ \link{https://github.com/MarvinMartin24}{Github} \\ \link{https://medium.com/@martin.marvin}{Medium}}

\begin{document}
	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Education}
		\begin{school}{Ecole Centrale d'Electronique de Paris}{Engineering School, Paris}{Sept 2018}{\em Present}{
			Information system, Operating Systems, Mathematics, Machine Learning, Big Data and Management  - Grade A ( 16,01/20 )
		}
		\end{school}

		\begin{school}{INSEEC London}{Engineering School, London}{Jan 2019}{May 2019}{
			Java, Image Processing, Probability and Statistics , Blockchain, Public Speaking - Grade A ( 17,32/20 )
		}
		\end{school}
		
		\begin{school}{Heriot-Watt University}{University, Edinburgh }{Jan 2018}{Jun 2018}{
			Electronics , Electric Circuits and Machines, C Language, Business Management - Grade A ( 17,08/20 )
		}
		\end{school}

		\begin{school}{Institut Supérieur d'Electronique de Paris}{Engineering School, Paris}{Sept 2016}{Dec 2018}{
			Python, Signal Processing (Matlab) , Mechanics Physics, Calculus \& Linear Algebra
		}
		\end{school}
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	WORK EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Experience}
		%----------------------------------------------------
		%	HEURITECH
		%----------------------------------------------------
		\begin{job}{Training Data Operator Intern}{Heuritech}{Paris, FR}{Apr 2020}{Aug 2020}{
			\link{hhttps://www.heuritech.com/}{Heuritech}  builds cutting-edge visual recognition and trend forecasting technologies using social media images. I  have industrialised Deep Learning solutions with Data Engineering and DevOps tasks in the Delivery Team. I developed internal automation tools, improved training datasets using Active Learning, trained and investigate Deep Learning models.}
		\end{job}
		%----------------------------------------------------
		%	LECTRA
		%----------------------------------------------------
		\begin{job}{Lab Intern}{Lectra Innovation Lab}{Bordeaux , FR}{Mai 2019}{Jun 2019}{
			\link{https://www.lectra.com/fr}{Lectra} develops  premium technologies that facilitate the digital transformation in the Fashion, Automotive, Furniture and Aeronautic Industries. I worked on Deep Learning projects (Generative Adversarial Network) and Data Mining programs. I also met startups at Vivatech 2019 for Business purpose.
		}
		\end{job}

		%----------------------------------------------------
		%	Timeo
		%----------------------------------------------------
		\begin{job}{Comedian - Musical }{Timéo}{Paris, FR}{Nov 2015}{Jan 2017}{
			\link{https://www.youtube.com/channel/UCorBR38MbWKo92Go3dBpv2Q}{Timéo (Casino de Paris)} is the story of a young disabled person who becomes an artist despite his disability. The show spread a message of tolerance towards differences. I was Michael a skateboarder, the bad boy at school that bullied Timeo.}
		\end{job}
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%	SKILLS
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Skills}
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			Programming &  Python, JavaScript (Reactjs), Java, Swift, C Language, SQL, MongoDB\\
			DevOps &  UNIX, Git, Docker\\
			General &  Mathematics, Physics, Deep Learning\\
			Social & Leadership, Public Speaking
		\end{tabular}
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%	Certificate
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Certificate}
		\link{	https://www.coursera.org/account/accomplishments/specialization/certificate/925K8YUCXEW2}{Coursera}  Deep Learning Specialization by Andrew Ng\\
		\link{	https://www.udemy.com/certificate/UC-828742bf-b681-48ca-8715-8879de561696/}{Udemy}  Deep Learning and Computer Vision A-Z™: OpenCV, SSD and GANs\\
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%	LANGUAGES
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Languages}
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			French &  Fluent (Certificat Voltaire - Score: 790) \\
			English &  Fluent (IELTS - Score: 7 and TOIEC - Score: 800) \\
			Spanish &  Limited professional competence \\
			Chinese &  Basic notions  (HSK1 - Score: 124)\\
		\end{tabular}
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	EXTRA
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Extracurriculars}
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			Activities  & Skateboard instructor (BIF - French diploma), Mannequin\\
			Interests & High Level Skateboarding, Surf, Snowboard, Slackline, Guitar, Writing Articles and Fashion\\
		\end{tabular}
	\end{rSection}
	
\end{document}
